---
title: "Power test"
author: "Morera-Pujol, Virginia"
date: "July 2021"
output: html_document
---

## Power analysis for the ISF test

Testing the ability of the `indEffectTest()` function to detect ISF. The function was developed for the *Detecting recurrent sources of variability in animal tracking studies* manuscript by Virginia Morera-Pujol *et al.* submitted to Ecological Applications in 2021

### Description

In this document, I will use the simulated datasets obtained following the steps in the *Demo_simulating_ISF_tracks* document, and the procedure described in the *Testing_IndEffectTest_function* document, to run the function over a sequence of datasets with increasing levels of individual site fidelity for data of both colonial and non-colonial simulated "species". To simulate the different degrees of ISF we change the resistance of the layer outside the "allowed" polygon.

```{r setup, include = F}
knitr::opts_knit$set(echo = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, 
                     cache = TRUE, fig.width = 12, fig.height = 8)

install.packages("pacman", repos = "http://cran.us.r-project.org")
pacman::p_load(tidyverse, plyr, adehabitatHR, Matching, sf, ctmm, doParallel, foreach, ggpubr,
               geosphere, RColorBrewer, gridExtra, lubridate, SiMRiv, kableExtra)

'%!in%' <- function(x,y)!('%in%'(x,y))
```

## For animals with different origins

### Generating the data

For more detail on this procedure, see the *Demo_simulating_ISF_tracks* in this repository

```{r PowerTest generate, results = 'hide', message = FALSE, warning = FALSE, fig.show = 'hide', cache = TRUE, eval = F}
set.seed(2020)
CRW <- species(state.CRW(0.2))
test <- simulate(CRW, coords = c(0, 0), time = 100)

# create empty base raster for resistance surfaces
baseRaster <- raster(xmn = -50, xmx = 50, ymn = -50, ymx = 50, res = 0.1)
values(baseRaster) <- 1
baseGrid <- as(baseRaster, "SpatialPixels")

# create an set of random origin points
origin_points <- data.frame(x = runif(10, -25, 25), 
                            y = runif(10, -25, 25))

# simulate 10 trips for each origin (i.e. 10 trips per individual)
template_tracks <- list()
template_UDs <- list()
resistance_surfaces <- list()
simulated_tracks <- list()

plot(1, xlim = c(-50, 50), ylim = c(-50, 50), type = "n", 
     main = "All the 'template' tracks")

# 
resistances <- c(1, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1, 0)

for (j in seq_along(resistances)) {
  # j = 5 
  res <- resistances[j]
  
  for (i in 1:10) {
    # i = 1
    
    # First we need to create a template trip to get the UD for the resistance surface
    template <- simulate(CRW, coords = c(origin_points[i,1], origin_points[i, 2]), 
                       time = 100)
    template_tracks[i] <- list(template)
    lines(template, col = brewer.pal(10,"Set3")[i])
    points(template, col = brewer.pal(10,"Set3")[i], pch = 16)
    spTemplate <- SpatialPoints(coords = template[,1:2], proj4string = baseGrid@proj4string)
    KDE <- kernelUD(spTemplate, h = "href", grid = baseGrid) 
    UD50 <- getverticeshr(KDE, percent = 50)
    template_UDs[i] <- list(UD50) 
    # plot(KDE)
    # plot(UD50, add = T)
    # plot(spTemplate, pch = 20, cex = 0.5, add = T)
    
    # Second, we create the resistance surface
    res_surface <- resistanceFromShape(UD50, baseRaster = baseRaster, field = 0, 
                                       binary = F, background = 1)
    res_surface[res_surface == 1] <- res
    # plot(res_surface)
    resistance_surfaces[i] <- list(res_surface)
    # plot(res_surface)
    
    # Third, we simulate 10 tracks from each surface (i.e. from each individual)
    sim_tracks <- simulate(list(CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW), 
                           start.resistance	= 0,
                           time = 100, resist = res_surface)
    spSim <- SpatialPointsDataFrame(coords = cbind(c(sim_tracks[,1], sim_tracks[,4],
                                                     sim_tracks[,7], sim_tracks[,10],
                                                     sim_tracks[,13], sim_tracks[,16],
                                                     sim_tracks[,19], sim_tracks[,22],
                                                     sim_tracks[,25],sim_tracks[,28]),
                                                   c(sim_tracks[,2], sim_tracks[,5],
                                                     sim_tracks[,8], sim_tracks[,11],
                                                     sim_tracks[,14],sim_tracks[,17],
                                                     sim_tracks[,20], sim_tracks[,23],
                                                     sim_tracks[,26], sim_tracks[,29])), 
                                    data = data.frame(TrackID = paste(i, rep(1:10, 
                                                                             each = 100),
                                                                      sep = "_"), 
                                                      BirdID = rep(i, 1000)))
    spSim@proj4string <- baseGrid@proj4string
    simulated_tracks[i] <- list(spSim)
    spSim$BirdID <- NULL
    # KUD_sim <- kernelUD(spSim, grid = baseGrid)
    # print(mean(kerneloverlap(spSim, method = "BA", percent = 50, conditional = T)))
    # plot(spSim, add = T, col = factor(spSim$TrackID), pch = ".", cex = 0.1)
  }
  
  list.df <- lapply(seq_along(simulated_tracks),
                    function(i){simulated_tracks[i][[1]]})
  
  # apply rbind to the list
  simulated_dataset <- do.call("rbind",
                               list.df)
  
  # assign null projection as X/Y values don't mean anything in this case
  simulated_dataset@proj4string <- CRS(as.character(NA))
  save(simulated_dataset, file = paste0("simulated_dataset_noncolonial_res", res, ".RDS"))
}
```

### Testing the function

Plot first all the datasets used for the powertest

```{r PowerTest plots, message = FALSE, warning = FALSE, fig.width = 15, fig.height = 15}
# plot the different datasets to compare ISF visually
rdslist <- list.files(pattern = ".RDS")

rdslist <- rdslist[grepl('simulated_dataset_noncolonial', rdslist)]
plotlist <- list()
# for (j in c(10, 1, 2, 3, 4, 5, 6, 7, 8, 9, 11)) {
for(j in seq_along(rdslist)){  
  # j = 10
  
  load(rdslist[j])
  sds <- as.data.frame(simulated_dataset)

  sds %>% 
    dplyr::group_by(TrackID) %>%
    dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), 
                                  ymd_hms('2020-01-30 12:10:00'), 
                                  length.out = 100)) %>% 
    mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>% 
    dplyr::select(individual.local.identifier = TrackID, 
                  Longitude = coords.x1, Latitude = coords.x2, 
                  datetime = Date_Time) %>% 
    ungroup() -> sds
  sds <- as.data.frame(sds)
  
  sdf <- sds %>% 
    separate(individual.local.identifier, c("Ind", "Trip")) %>% 
    st_as_sf(coords = c("Longitude", "Latitude")) %>% 
    mutate(Ind = factor(as.character(Ind), levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10))) %>% 
    mutate(Trip = factor(as.character(Trip), levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)))
  plot_title <- paste0("Outside resistance ", 
                       gsub("res", "", 
                            strsplit(tools::file_path_sans_ext(rdslist[j]), "_")[[1]][[4]]))
  
  plt <- ggplot() + 
    geom_sf(data = sdf, aes(col = Ind), alpha = 0.3, size = 0.7) + 
    xlab("") + ylab("") +
    theme_bw() + 
    theme_bw() + 
    theme(legend.position = "right", legend.box = "horizontal") + 
    guides(col = guide_legend(override.aes = list(size = 3, alpha = 1))) +
    coord_sf(xlim = c(-50, 50),
             ylim = c(-50, 50), expand = T) +
    # scale_shape(guide = "none") +
    ggtitle(plot_title)
    NULL
  plotlist[j] <- list(plt)
  names(plotlist)[j] <- plot_title
  # print(plt)
  rm(simulated_dataset)
}

plotlist <- plotlist[
  c("Outside resistance 0", "Outside resistance 0.1", "Outside resistance 0.2", 
           "Outside resistance 0.3", "Outside resistance 0.4", "Outside resistance 0.5",
           "Outside resistance 0.6", "Outside resistance 0.7", "Outside resistance 0.8",
           "Outside resistance 0.9", "Outside resistance 1")]
ggpubr::ggarrange(plotlist = plotlist, common.legend = T)

```

We now run a simplified version of the function `IndEffectTest` without all the code re the spatial projection, crossing datelines, etc. and as plain code outside the function for easy tweaking.

```{r PowerTest fun1, message = FALSE, warning = FALSE, eval = FALSE}
# To calculate the overlap we:
# 1 - Turn simulated tracks into "telemetry" objects"
# 2 - fit a guesstimate movement model to each track
# 3 - using the parameters of the guesstimate, fit a series of competing movement models
# 4 - Calculate the debiased BA between top-selected models for each track
# (uncertainty from the model fits is propagated into the overlap estimate under the
#     approximation that the BA is a chi-square random variable)

cl <- makeCluster(10, type="PSOCK") ## specify number of cores, and type of cluster (PSOCK or FORK)
registerDoParallel(cl) ## register the backend into a virtual node

# results_list <- list()
## Execute parallel operation
results_list <- foreach(j = 1:11, .packages=c("dplyr", "ctmm", "ggplot2", "lubridate")) %dopar% {
          # for (j in seq_along(rdslist)) {
          Result <- list()
          # j = 1
          load(rdslist[j])
  sds <- as.data.frame(simulated_dataset)

  sds %>% 
    dplyr::group_by(TrackID) %>%
    dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), 
                                  ymd_hms('2020-01-30 12:10:00'), 
                                  length.out = 100)) %>% 
    mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>% 
    dplyr::select(individual.local.identifier = TrackID, 
                  Longitude = coords.x1, Latitude = coords.x2, 
                  datetime = Date_Time) %>% 
    ungroup() -> sds
  
  sds <- as.data.frame(sds)
  # 1
  sd_tel <- as.telemetry(object = sds, timeformat = "%Y/%m/%d %H:%M:%S")
  
  
  FIT.list <- list()
  
  before <- Sys.time()
  
  for(i in 1:length(sd_tel)){
  # for(i in 1:10){
    print(i)
    one <- sd_tel[[i]]
    # 2
    GUESS <- ctmm.guess(one, interactive=F)
    # 3
    FITS <- ctmm.select(one, GUESS,  trace=TRUE, verbose=TRUE, cores=0)
    print(paste("The selected model for", names(sd_tel)[i], "is", names(FITS)[1], sep = " "))
    FIT.list[[i]] <- FITS[[1]]
  }
  Sys.time() - before
  
  # 4
  ov <- ctmm::overlap(FIT.list, level = 0.95)
  
  # we select the "middle layer" of the array which contains the point estimate 
  # (for now ignoring the CI)
  X05 <- ov[,,2]
  Xlo <- ov[,,1]
  Xhi <- ov[,,3]
  
  X05[lower.tri(X05, diag = T)] <- NA
  Xlo[lower.tri(Xlo, diag = T)] <- NA
  Xhi[lower.tri(Xhi, diag = T)] <- NA
  
  Result[1] <- list(list(X05, Xlo, Xhi))
  # assign value of BirdID that we rescue from the simulated_dataset df to rows and columns
  gid <- simulated_dataset@data[!duplicated(simulated_dataset@data[, "TrackID"]), ][["BirdID"]]
  rownames(X05) <- colnames(X05) <- gid
  rownames(Xlo) <- colnames(Xlo) <- gid
  rownames(Xhi) <- colnames(Xhi) <- gid
  
  # separate within (WI) and between (BW) group overlaps
  
  # median
  WI05 <- NULL
  BW05 <- NULL
  
  # lower
  WIlo <- NULL
  BWlo <- NULL
  
  # higher
  WIhi <- NULL
  BWhi <- NULL
  
  for (i in seq_along(rownames(X05))) {
    # i = 1
    
    # medians
    x1 <- X05[i,] 
    x2 <- x1[which(names(x1) == rownames(X05)[i])]
    x3 <- x1[which(names(x1) != rownames(X05)[i])]
    WI05 <- c(WI05, x2)
    BW05 <- c(BW05, x3)
    
    # BW intervals
    x1 <- Xlo[i,] 
    x3 <- x1[which(names(x1) != rownames(Xlo)[i])]
    BWlo <- c(BWlo, x3)
    
    x1 <- Xhi[i,] 
    x3 <- x1[which(names(x1) != rownames(Xhi)[i])]
    BWhi <- c(BWhi, x3)
    
  }
  
  # medians
  BW05 <- BW05[!is.na(BW05)]
  WI05 <- WI05[!is.na(WI05)]
  
  # BW intervals
  BWlo <- BWlo[!is.na(BWlo)]
  BWhi <- BWhi[!is.na(BWhi)]
  
  # organize values in a dataframe for plotting
  Overlaps <- data.frame(
    Overlap = c(WI05, BW05),
    Type = c(rep("Within", length(WI05)), rep("Between", length(BW05))),
    Test = rdslist[j]
    )
  Result[2] <- list(Overlaps)
  # plot boxplot
  
  plot1 <- ggplot(data = Overlaps) + 
    geom_density(aes(x = Overlap, col = Type, fill = Type), alpha = 0.5) + 
    ggtitle("Density of within individual vs. between individual median overlaps") +
    theme_bw()
  
  Result[3] <- list(plot1)
  
  
  WI_median <- quantile(WI05, 0.5)
  
  BWint <- data.frame(Low = BWlo,
                      High = BWhi)
  
  BWint <- BWint %>% 
    mutate(Contains = "NA") %>% 
    mutate(Contains = if_else(High > WI_median, "NotAbove", "Above"))
  
  proportions <- as.data.frame(prop.table(table(BWint$Contains)))
  
  names(proportions) <- c("WI_Median_Position", "Percentage")
  proportions$Percentage <- round(proportions$Percentage*100, 1)
  
  Result[4] <- list(proportions)
  
  # results_list[j] <- list(Result)
  
  save(FIT.list, ov, Result, 
       file = paste("noncolonial_powerTest", strsplit(rdslist[j], "_")[[1]][4], sep = "_"))
}
stopCluster(cl)

```

### Explore sensitivity tests outputs

```{r ISF test2 output}
powertestfiles <- list.files(pattern = "noncolonial_powerTest")

res_list <- list()
plot_list <- list()
for(i in c(10, 1, 2, 3, 4, 5, 6, 7, 8, 9, 11)) {
  # i = 10
  load(powertestfiles[i])
  Test = str_sub(powertestfiles[i], end = -5)
  res <- Result[[4]]
  res2 <- cbind(Test, res)
  res_list[i] <- list(res2)
  plot_list[i] <- list(Result[[3]])
  names(plot_list)[i] <- Test
}

test_results <- bind_rows(res_list)

test_results %>% 
  pivot_wider(names_from = "WI_Median_Position", values_from = "Percentage") %>% 
  separate(Test, into = c("Type of test", "test", "Resistance"), sep = "_", remove = T) %>% 
  mutate(Resistance = as.numeric(gsub("res", "", Resistance))) %>% 
  arrange(Resistance) %>% 
  dplyr::select("Resistance", "Above (WBR)" = "Above", "NotAbove") %>% 
  kable(digits = 2, align = "rrrr", caption = "Power Test - noncolonial") %>%
  kable_classic(full_width = F, html_font = "Cambria")

```

## For animals with the same origin

### Generating the data

For more detail on this procedure, see the *Demo_simulating_ISF_tracks* in this repository

```{r PowerTest2 generate, results = 'hide', message = FALSE, warning = FALSE, fig.show = 'hide', cache = TRUE, eval = FALSE}
set.seed(205)
CRW <- species(state.CRW(0.1))
test <- simulate(CRW, coords = c(0, 0), time = 100)

# create empty base raster for resistance surfaces
baseRaster <- raster(xmn = -70, xmx = 70, ymn = -70, ymx = 70, res = 0.1)
values(baseRaster) <- 1
baseGrid <- as(baseRaster, "SpatialPixels")

# create a vector of random angles
angles <- runif(10, 0, 360)

# simulate 10 trips for each origin (i.e. 10 trips per individual)
template_tracks <- list()
template_UDs <- list()
resistance_surfaces <- list()
simulated_tracks <- list()

plot(1, xlim = c(-70, 70), ylim = c(-70, 70), type = "n", 
     main = "All the 'template' tracks")

resistances <- c(1, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1, 0)

for (j in seq_along(resistances)) {
  # j = 11
  res <- resistances[j]
  
  for (i in 1:10) {
    # i = 1
    
    # First we need to create a template trip to get the UD for the resistance surface
    template <- simulate(CRW, coords = c(0, 0), angles = angles[i], time = 1000)
    template <- as.data.frame(template)
    template <- template %>% 
      filter(V1 > -60 & V1 < 60) %>% 
      filter(V2 > -60 & V2 < 60)
    
    template_tracks[i] <- list(template)
    lines(template, col = brewer.pal(10,"Set3")[i])
    points(template, col = brewer.pal(10,"Set3")[i], pch = 16)
    spTemplate <- SpatialPoints(coords = template[,1:2], proj4string = baseGrid@proj4string)
    
    print(i)
    KDE <- kernelUD(spTemplate, h = "href", grid = baseGrid, extent = 2) 
    UD50 <- getverticeshr(KDE, percent = 50)
    template_UDs[i] <- list(UD50) 
    
    # Second, we create the resistance surface
    res_surface <- resistanceFromShape(UD50, baseRaster = baseRaster, field = 0, 
                                       binary = F, background = 1)
    res_surface[res_surface == 1] <- res
    resistance_surfaces[i] <- list(res_surface)
    
    # Third, we simulate 10 tracks from each surface (i.e. from each individual)
    sim_tracks <- simulate(list(CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW), 
                           start.resistance	= 0,
                           time = 100, resist = res_surface)
    spSim <- SpatialPointsDataFrame(coords = cbind(c(sim_tracks[,1], sim_tracks[,4],
                                                     sim_tracks[,7], sim_tracks[,10],
                                                     sim_tracks[,13], sim_tracks[,16],
                                                     sim_tracks[,19], sim_tracks[,22],
                                                     sim_tracks[,25],sim_tracks[,28]),
                                                   c(sim_tracks[,2], sim_tracks[,5],
                                                     sim_tracks[,8], sim_tracks[,11],
                                                     sim_tracks[,14],sim_tracks[,17],
                                                     sim_tracks[,20], sim_tracks[,23],
                                                     sim_tracks[,26], sim_tracks[,29])), 
                                    data = data.frame(TrackID = paste(i, rep(1:10, 
                                                                             each = 100),
                                                                      sep = "_"), 
                                                      BirdID = rep(i, 1000)))
    spSim@proj4string <- baseGrid@proj4string
    simulated_tracks[i] <- list(spSim)
    spSim$BirdID <- NULL
  }
  
  list.df <- lapply(seq_along(simulated_tracks),
                    function(i){simulated_tracks[i][[1]]})
  
  # apply rbind to the list
  simulated_dataset <- do.call("rbind",
                               list.df)
  
  # assign null projection as X/Y values don't mean anything in this case
  simulated_dataset@proj4string <- CRS(as.character(NA))
  save(simulated_dataset, file = paste0("simulated_dataset_colonial_res", res, ".RDS"))
}
```

### Testing the function

Plot first all the datasets used for the powertest

```{r PowerTest plots2, message = FALSE, warning = FALSE, fig.width = 15, fig.height = 15}
# plot the different datasets to compare ISF visually
rdslist <- list.files(pattern = ".RDS")

rdslist <- rdslist[grepl('simulated_dataset_colonial', rdslist)]

plotlist <- list()
for (j in seq_along(rdslist)) {
  # j = 1
  
  load(rdslist[j])
  sds <- as.data.frame(simulated_dataset)

  sds %>% 
    dplyr::group_by(TrackID) %>%
    dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), 
                                  ymd_hms('2020-01-30 12:10:00'), 
                                  length.out = 100)) %>% 
    mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>% 
    dplyr::select(individual.local.identifier = TrackID, 
                  Longitude = coords.x1, Latitude = coords.x2, 
                  datetime = Date_Time) %>% 
    ungroup() -> sds
  sds <- as.data.frame(sds)
  
  sdf <- sds %>% 
    separate(individual.local.identifier, c("Ind", "Trip")) %>% 
    st_as_sf(coords = c("Longitude", "Latitude")) %>% 
    mutate(Ind = factor(as.character(Ind), levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10))) %>% 
    mutate(Trip = factor(as.character(Trip), levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)))
  
  plot_title <- paste0("Outside resistance ", 
                       gsub("res", "", 
                            strsplit(tools::file_path_sans_ext(rdslist[j]), "_")[[1]][[4]]))
  
  plt <- ggplot() + 
    geom_sf(data = sdf, aes(col = Ind), alpha = 0.3, size = 0.7) + 
    xlab("") + ylab("") +
    theme_bw() + 
    theme_bw() + 
    theme(legend.position = "right", legend.box = "horizontal") + 
    guides(col = guide_legend(override.aes = list(size = 3, alpha = 1))) +
    coord_sf(xlim = c(-50, 50),
             ylim = c(-50, 50), expand = T) +
    # scale_shape(guide = "none") +
    ggtitle(plot_title)
    NULL
  plotlist[j] <- list(plt)
  names(plotlist)[j] <- plot_title
  # print(plt)
  rm(simulated_dataset)
}

plotlist <- plotlist[
  c("Outside resistance 0", "Outside resistance 0.1", "Outside resistance 0.2", 
           "Outside resistance 0.3", "Outside resistance 0.4", "Outside resistance 0.5",
           "Outside resistance 0.6", "Outside resistance 0.7", "Outside resistance 0.8",
           "Outside resistance 0.9", "Outside resistance 1")]
ggpubr::ggarrange(plotlist = plotlist, common.legend = T)

```

We now run a simplified version of the function `IndEffectTest` without all the code re the spatial projection, crossing datelines, etc. and as plain code outside the function for easy tweaking.

```{r PowerTest2 fun1, message = FALSE, warning = FALSE, eval = FALSE}
# To calculate the overlap we:
# 1 - Turn simulated tracks into "telemetry" objects"
# 2 - fit a guesstimate movement model to each track
# 3 - using the parameters of the guesstimate, fit a series of competing movement models
# 4 - Calculate the debiased BA between top-selected models for each track
# (uncertainty from the model fits is propagated into the overlap estimate under the
#     approximation that the BA is a chi-square random variable)
rdslist <- list.files(pattern = ".RDS")

rdslist <- rdslist[grepl('simulated_dataset_colonial', rdslist)]

cl <- makeCluster(10, type="PSOCK") ## specify number of cores, and type of cluster (PSOCK or FORK)
registerDoParallel(cl) ## register the backend into a virtual node

# results_list <- list()
## Execute parallel operation
results_list <- foreach(j = 1:11, .packages=c("dplyr", "ctmm", "ggplot2", "lubridate")) %dopar% {
  Result <- list()
  # j = 1
  
  load(rdslist[j])
  sds <- as.data.frame(simulated_dataset)

  sds %>% 
    dplyr::group_by(TrackID) %>%
    dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), 
                                  ymd_hms('2020-01-30 12:10:00'), 
                                  length.out = 100)) %>% 
    mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>% 
    dplyr::select(individual.local.identifier = TrackID, 
                  Longitude = coords.x1, Latitude = coords.x2, 
                  datetime = Date_Time) %>% 
    ungroup() -> sds
  
  sds <- as.data.frame(sds)
  # 1
  sd_tel <- as.telemetry(object = sds, timeformat = "%Y/%m/%d %H:%M:%S")
  
  
  FIT.list <- list()
  
  before <- Sys.time()
  
  for(i in 1:length(sd_tel)){
    print(i)
    one <- sd_tel[[i]]
    # 2
    GUESS <- ctmm.guess(one, interactive=F)
    # 3
    FITS <- ctmm.select(one, GUESS,  trace=TRUE, verbose=TRUE, cores=0)
    print(paste("The selected model for", names(sd_tel)[i], "is", names(FITS)[1], sep = " "))
    FIT.list[[i]] <- FITS[[1]]
  }
  Sys.time() - before
  
  # 4
  ov <- ctmm::overlap(FIT.list, level = 0.95)

  # we select the "middle layer" of the array which contains the point estimate 
  # (for now ignoring the CI)
  X05 <- ov[,,2]
  Xlo <- ov[,,1]
  Xhi <- ov[,,3]
  
  X05[lower.tri(X05, diag = T)] <- NA
  Xlo[lower.tri(Xlo, diag = T)] <- NA
  Xhi[lower.tri(Xhi, diag = T)] <- NA
  
  Result[1] <- list(list(X05, Xlo, Xhi))
  # assign value of BirdID that we rescue from the simulated_dataset df to rows and columns
  gid <- simulated_dataset@data[!duplicated(simulated_dataset@data[, "TrackID"]), ][["BirdID"]]
  rownames(X05) <- colnames(X05) <- gid
  rownames(Xlo) <- colnames(Xlo) <- gid
  rownames(Xhi) <- colnames(Xhi) <- gid
  
  # separate within (WI) and between (BW) group overlaps
  
  # median
  WI05 <- NULL
  BW05 <- NULL
  
  # lower
  WIlo <- NULL
  BWlo <- NULL
  
  # higher
  WIhi <- NULL
  BWhi <- NULL
  
  for (i in seq_along(rownames(X05))) {
    # i = 1
    
    # medians
    x1 <- X05[i,] 
    x2 <- x1[which(names(x1) == rownames(X05)[i])]
    x3 <- x1[which(names(x1) != rownames(X05)[i])]
    WI05 <- c(WI05, x2)
    BW05 <- c(BW05, x3)
    
    # BW intervals
    x1 <- Xlo[i,] 
    x3 <- x1[which(names(x1) != rownames(Xlo)[i])]
    BWlo <- c(BWlo, x3)
    
    x1 <- Xhi[i,] 
    x3 <- x1[which(names(x1) != rownames(Xhi)[i])]
    BWhi <- c(BWhi, x3)
    
  }
  
  # medians
  BW05 <- BW05[!is.na(BW05)]
  WI05 <- WI05[!is.na(WI05)]
  
  # BW intervals
  BWlo <- BWlo[!is.na(BWlo)]
  BWhi <- BWhi[!is.na(BWhi)]
  
  # organize values in a dataframe for plotting
  Overlaps <- data.frame(
    Overlap = c(WI05, BW05),
    Type = c(rep("Within", length(WI05)), rep("Between", length(BW05))),
    Test = rdslist[j]
    )
  Result[2] <- list(Overlaps)

  plot1 <- ggplot(data = Overlaps) + 
    geom_density(aes(x = Overlap, col = Type, fill = Type), alpha = 0.5) + 
    ggtitle("Density of within individual vs. between individual median overlaps") +
    theme_bw()
  
  Result[3] <- list(plot1)
  
  
  WI_median <- quantile(WI05, 0.5)
  
  BWint <- data.frame(Low = BWlo,
                      High = BWhi)
  
  BWint <- BWint %>% 
    mutate(Contains = "NA") %>% 
    mutate(Contains = if_else(High > WI_median, "Above", "NotAbove"))
  
  proportions <- as.data.frame(prop.table(table(BWint$Contains)))
  
  names(proportions) <- c("WI_Median_Position", "Percentage")
  proportions$Percentage <- round(proportions$Percentage*100, 1)
  
  Result[4] <- list(proportions)
  
  results_list[j] <- list(Result)
  
  save(FIT.list, ov, Result, 
       file = paste("colonial_powerTest", strsplit(rdslist[j], "_")[[1]][4], sep = "_"))
}
stopCluster(cl)
```

### Explore sensitivity tests outputs

```{r PowerTest2 results}
powertestfiles <- list.files(pattern = "^colonial_powerTest")

res_list <- list()
plot_list <- list()
for(i in seq_along(powertestfiles)) {
  # i = 1
  load(powertestfiles[i])
  Test = str_sub(powertestfiles[i], end = -5)
  res <- Result[[4]]
  res2 <- cbind(Test, res)
 res_list[i] <- list(res2)
 plot_list[i] <- list(Result[[3]])
 names(plot_list)[i] <- Test
}

test_results <- bind_rows(res_list)

test_results %>% 
  pivot_wider(names_from = "WI_Median_Position", values_from = "Percentage") %>% 
  separate(Test, into = c("Type of test", "test", "Resistance"), sep = "_", remove = T) %>% 
  mutate(Resistance = as.numeric(gsub("res", "", Resistance))) %>% 
  arrange(Resistance) %>% 
  dplyr::select("Resistance", "Above (WBR)" = "Above", "NotAbove") %>% 
  kable(digits = 2, align = "rrrr", caption = "Power Test - colonial") %>%
  kable_classic(full_width = F, html_font = "Cambria")
  
```
