---
title: "Effect of sampling frequency on ISF test"
author: "Virginia Morera-Pujol"
date: "May 2021"
output: html_document
---

## Sampling frequency test

Testing the ability of the IndEffectTest function to detect ISF at different sampling frequencies. The test was developed for the *Detecting recurrent sources of variability in animal tracking studies* manuscript by Virginia Morera-Pujol *et al.* submitted to Ecological Applications in 2021

### Description

Here, we use the dataset of the non-colonial simulated species with a 1 resistance surface (high ISF). From it, we will subset every fifth position, and then every tenth, and compare the results of the individual site fidelity test. 

```{r setup, include = F}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, 
                      fig.width = 12, fig.height = 8)
knitr::opts_knit$set(root.dir = "C:/Users/Virginia/Dropbox/Virginia/GLS_multi/PowerTest")

# setwd("C:/Users/Virginia/Dropbox/Virginia/GLS_multi/PowerTest")

pacman::p_load(tidyverse, plyr, adehabitatHR, Matching, sf, ctmm,
               geosphere, RColorBrewer, gridExtra, lubridate, SiMRiv)
  
'%!in%' <- function(x,y)!('%in%'(x,y))

load("C:/Users/Virginia/Dropbox/Virginia/GLS_multi/PowerTest/simulated_dataset_noncolonial_res1.RDS")
```

#### First test ISF with the full simulated dataset of high ISF

```{r, cache = TRUE, message = FALSE, warning = FALSE, collapse = TRUE}
sds <- as.data.frame(simulated_dataset)

sds %>% 
  dplyr::group_by(TrackID) %>%
  dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), ymd_hms('2020-01-30 12:10:00'), 
                                length.out = 100)) %>% 
  mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>% 
  dplyr::select(individual.local.identifier = TrackID, 
                Longitude = coords.x1, Latitude = coords.x2, 
                datetime = Date_Time) %>% 
  ungroup() -> sds
sds <- as.data.frame(sds)

message_filename = "output_fullds.txt"
try(message_file <- file(message_filename, open="at")) # open file for appending in text mode
sink(message_file, type="message")
sink(message_file, type="output")
sd_tel <- as.telemetry(object = sds, timeformat = "%Y/%m/%d %H:%M:%S")


FIT.list <- list()

before <- Sys.time()
for(i in 1:length(sd_tel)){
  # print(i)
  one <- sd_tel[[i]]
  # 2
  GUESS <- ctmm.guess(one, interactive=F)
  # 3
  FITS <- ctmm.select(one, GUESS,  trace=TRUE, verbose=TRUE, cores=-1)
  # print(paste("The selected model for", names(sd_tel)[i], "is", names(FITS)[1], sep = " "))
  FIT.list[[i]] <- FITS[[1]]
}
sink(file = NULL, type="message")
sink(file = NULL, type="output")
# closeAllConnections() 
Sys.time() - before

# 4
ov <- ctmm::overlap(FIT.list, level = 0.95)

# separate the layers of the median and CI
X05 <- ov[,,2]
Xlo <- ov[,,1]
Xhi <- ov[,,3]

# remove lower triangle of each (repeated values since it's a symetric matrix)
X05[lower.tri(X05, diag = T)] <- NA
Xlo[lower.tri(Xlo, diag = T)] <- NA
Xhi[lower.tri(Xhi, diag = T)] <- NA


# assign value of BirdID that we rescue from the simulated_dataset df to rows and columns
gid <- simulated_dataset@data[!duplicated(simulated_dataset@data[, "TrackID"]), ][["BirdID"]]
rownames(X05) <- colnames(X05) <- gid
rownames(Xlo) <- colnames(Xlo) <- gid
rownames(Xhi) <- colnames(Xhi) <- gid

# median
WI05 <- NULL
BW05 <- NULL

# BW lower and higher CI bounds
BWlo <- NULL
BWhi <- NULL

for (i in seq_along(rownames(X05))) {
  # i = 2
  
  # medians
  x1 <- X05[i,] 
  x2 <- x1[which(names(x1) == rownames(X05)[i])]
  x3 <- x1[which(names(x1) != rownames(X05)[i])]
  
  WI05 <- c(WI05, x2)
  BW05 <- c(BW05, x3)
  
  # BW intervals
  y1 <- Xlo[i,] 
  y2 <- y1[which(names(y1) != rownames(Xlo)[i])]
  BWlo <- c(BWlo, y2)
  
  z1 <- Xhi[i,] 
  z2 <- z1[which(names(z1) != rownames(Xhi)[i])]
  BWhi <- c(BWhi, z2)
  
}

# remove NAs
WI05 <- WI05[!is.na(WI05)]
BW05 <- BW05[!is.na(BW05)]
BWlo <- BWlo[!is.na(BWlo)]
BWhi <- BWhi[!is.na(BWhi)]

# organize values in a dataframe for plotting
Overlaps <- data.frame(
  Overlap = c(WI05, BW05),
  Type = c(rep("Within", length(WI05)), rep("Between", length(BW05)))
)

plotFull <- ggplot(data = Overlaps) + 
  geom_density(aes(x = Overlap, col = Type, fill = Type), alpha = 0.5) + 
  ggtitle("Full dataset") +
  theme_bw()

WI_median <- quantile(WI05, 0.5)

BWint <- data.frame(Low = BWlo,
                    High = BWhi)

BWint <- BWint %>% 
  mutate(Contains = "NA") %>% 
  mutate(Contains = if_else(High > WI_median, "NotAbove", "Above (WBR)"))

proportions <- as.data.frame(prop.table(table(BWint$Contains)))

names(proportions) <- c("WI_Median_Position", "Percentage")
proportions$Percentage <- round(proportions$Percentage*100, 2)

proportions_wide1 <- spread(proportions, WI_Median_Position, Percentage)

```


#### With the same dataset but subset just one every 5 positions

```{r, cache = TRUE, message = FALSE, warning = FALSE}

# turn to sf for easy subsetting and subset

sim_5th <- st_as_sf(simulated_dataset) %>%
  slice(which(row_number() %% 5 == 1))

sim_5th <- as_Spatial(sim_5th)

sds <- as.data.frame(sim_5th)

sds %>%
  dplyr::group_by(TrackID) %>%
  dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), ymd_hms('2020-01-30 12:10:00'),
                                length.out = 20)) %>%
  mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>%
  dplyr::select(individual.local.identifier = TrackID,
                Longitude = coords.x1, Latitude = coords.x2,
                datetime = Date_Time) %>%
  ungroup() -> sds

sds <- as.data.frame(sds)

message_filename = "output_5thds.txt"
try(message_file <- file(message_filename, open="at")) # open file for appending in text mode
sink(message_file, type="message")
sink(message_file, type="output")

# 1
sd_tel <- as.telemetry(object = sds, timeformat = "%Y/%m/%d %H:%M:%S")

FIT.list <- list()

before <- Sys.time()
for(i in 1:length(sd_tel)){
  # print(i)
  one <- sd_tel[[i]]
  # 2
  GUESS <- ctmm.guess(one, interactive=F)
  # 3
  FITS <- ctmm.select(one, GUESS,  trace=TRUE, verbose=TRUE, cores=-1)
  # print(paste("The selected model for", names(sd_tel)[i], "is", names(FITS)[1], sep = " "))
  FIT.list[[i]] <- FITS[[1]]
}
sink(file = NULL, type="message")
sink(file = NULL, type="output")
# closeAllConnections()
Sys.time() - before

# 4
ov <- ctmm::overlap(FIT.list, level = 0.95)

# separate the layers of the median and CI
X05 <- ov[,,2]
Xlo <- ov[,,1]
Xhi <- ov[,,3]

# remove lower triangle of each (repeated values since it's a symetric matrix)
X05[lower.tri(X05, diag = T)] <- NA
Xlo[lower.tri(Xlo, diag = T)] <- NA
Xhi[lower.tri(Xhi, diag = T)] <- NA


# assign value of BirdID that we rescue from the simulated_dataset df to rows and columns
gid <- simulated_dataset@data[!duplicated(simulated_dataset@data[, "TrackID"]), ][["BirdID"]]
rownames(X05) <- colnames(X05) <- gid
rownames(Xlo) <- colnames(Xlo) <- gid
rownames(Xhi) <- colnames(Xhi) <- gid

# median
WI05 <- NULL
BW05 <- NULL

# BW lower and higher CI bounds
BWlo <- NULL
BWhi <- NULL

for (i in seq_along(rownames(X05))) {
  # i = 2

  # medians
  x1 <- X05[i,]
  x2 <- x1[which(names(x1) == rownames(X05)[i])]
  x3 <- x1[which(names(x1) != rownames(X05)[i])]

  WI05 <- c(WI05, x2)
  BW05 <- c(BW05, x3)

  # BW intervals
  y1 <- Xlo[i,]
  y2 <- y1[which(names(y1) != rownames(Xlo)[i])]
  BWlo <- c(BWlo, y2)

  z1 <- Xhi[i,]
  z2 <- z1[which(names(z1) != rownames(Xhi)[i])]
  BWhi <- c(BWhi, z2)

}

# remove NAs
WI05 <- WI05[!is.na(WI05)]
BW05 <- BW05[!is.na(BW05)]
BWlo <- BWlo[!is.na(BWlo)]
BWhi <- BWhi[!is.na(BWhi)]

# organize values in a dataframe for plotting
Overlaps <- data.frame(
  Overlap = c(WI05, BW05),
  Type = c(rep("Within", length(WI05)), rep("Between", length(BW05)))
)

plot1 <- ggplot(data = Overlaps) +
  geom_density(aes(x = Overlap, col = Type, fill = Type), alpha = 0.5) +
  ggtitle("Every 5th position") +
  theme_bw()

WI_median <- quantile(WI05, 0.5)

BWint <- data.frame(Low = BWlo,
                    High = BWhi)

BWint <- BWint %>%
    mutate(Contains = "NA") %>%
    mutate(Contains = if_else(High > WI_median, "NotAbove", "Above (WBR)"))

proportions <- as.data.frame(prop.table(table(BWint$Contains)))

names(proportions) <- c("WI_Median_Position", "Percentage")
proportions$Percentage <- round(proportions$Percentage*100, 2)

proportions_wide2 <- spread(proportions, WI_Median_Position, Percentage)
```

#### With the same dataset but subset just one every 10 positions

```{r, cache = TRUE, message = FALSE, warning = FALSE}

# turn to sf for easy subsetting and subset

sim_10th <- st_as_sf(simulated_dataset) %>%
  slice(which(row_number() %% 10 == 1))

sim_10th <- as_Spatial(sim_10th)

sds <- as.data.frame(sim_10th)

sds %>%
  dplyr::group_by(TrackID) %>%
  dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), ymd_hms('2020-01-30 12:10:00'),
                                length.out = 10)) %>%
  mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>%
  dplyr::select(individual.local.identifier = TrackID,
                Longitude = coords.x1, Latitude = coords.x2,
                datetime = Date_Time) %>%
  ungroup() -> sds

sds <- as.data.frame(sds)

message_filename = "output_10thds.txt"
try(message_file <- file(message_filename, open="at")) # open file for appending in text mode
sink(message_file, type="message")
sink(message_file, type="output")
sd_tel <- as.telemetry(object = sds, timeformat = "%Y/%m/%d %H:%M:%S")

FIT.list <- list()

before <- Sys.time()
for(i in 1:length(sd_tel)){
  # print(i)
  one <- sd_tel[[i]]
  # 2
  GUESS <- ctmm.guess(one, interactive=F)
  # 3
  FITS <- ctmm.select(one, GUESS,  trace=TRUE, verbose=TRUE, cores=-1)
  # print(paste("The selected model for", names(sd_tel)[i], "is", names(FITS)[1], sep = " "))
  FIT.list[[i]] <- FITS[[1]]
}
sink(file = NULL, type="message")
sink(file = NULL, type="output")
# closeAllConnections()
Sys.time() - before

# 4
ov <- ctmm::overlap(FIT.list, level = 0.95)

# separate the layers of the median and CI
X05 <- ov[,,2]
Xlo <- ov[,,1]
Xhi <- ov[,,3]

# remove lower triangle of each (repeated values since it's a symetric matrix)
X05[lower.tri(X05, diag = T)] <- NA
Xlo[lower.tri(Xlo, diag = T)] <- NA
Xhi[lower.tri(Xhi, diag = T)] <- NA


# assign value of BirdID that we rescue from the simulated_dataset df to rows and columns
gid <- simulated_dataset@data[!duplicated(simulated_dataset@data[, "TrackID"]), ][["BirdID"]]
rownames(X05) <- colnames(X05) <- gid
rownames(Xlo) <- colnames(Xlo) <- gid
rownames(Xhi) <- colnames(Xhi) <- gid

# median
WI05 <- NULL
BW05 <- NULL

# BW lower and higher CI bounds
BWlo <- NULL
BWhi <- NULL

for (i in seq_along(rownames(X05))) {
  # i = 2

  # medians
  x1 <- X05[i,]
  x2 <- x1[which(names(x1) == rownames(X05)[i])]
  x3 <- x1[which(names(x1) != rownames(X05)[i])]

  WI05 <- c(WI05, x2)
  BW05 <- c(BW05, x3)

  # BW intervals
  y1 <- Xlo[i,]
  y2 <- y1[which(names(y1) != rownames(Xlo)[i])]
  BWlo <- c(BWlo, y2)

  z1 <- Xhi[i,]
  z2 <- z1[which(names(z1) != rownames(Xhi)[i])]
  BWhi <- c(BWhi, z2)

}

# remove NAs
WI05 <- WI05[!is.na(WI05)]
BW05 <- BW05[!is.na(BW05)]
BWlo <- BWlo[!is.na(BWlo)]
BWhi <- BWhi[!is.na(BWhi)]

# organize values in a dataframe for plotting
Overlaps <- data.frame(
  Overlap = c(WI05, BW05),
  Type = c(rep("Within", length(WI05)), rep("Between", length(BW05)))
)

plot2 <- ggplot(data = Overlaps) +
  geom_density(aes(x = Overlap, col = Type, fill = Type), alpha = 0.5) +
  ggtitle("Every 10th position") +
  theme_bw()

WI_median <- quantile(WI05, 0.5)

BWint <- data.frame(Low = BWlo,
                    High = BWhi)

BWint <- BWint %>%
    mutate(Contains = "NA") %>%
    mutate(Contains = if_else(High > WI_median, "NotAbove", "Above (WBR)"))

proportions <- as.data.frame(prop.table(table(BWint$Contains)))

names(proportions) <- c("WI_Median_Position", "Percentage")
proportions$Percentage <- round(proportions$Percentage*100, 2)

proportions_wide3 <- spread(proportions, WI_Median_Position, Percentage)
```

#### Compare the results

```{r, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 12}
final_df <- bind_rows(
  proportions_wide1, proportions_wide2, proportions_wide3
)

final_df$test <- c("original", "every_5th", "every_10th")

final_df %>%
  kable(digits = 2, align = "rrrr", caption = "Test sampling frequency") %>%
  kable_classic(full_width = F, html_font = "Cambria")
# write.csv(final_df, file = "compare_frequencies.csv", row.names = F)

# png(filename = "compare_frequencies.png", width = 15, height = 15*1.2, units = "cm", res = 900)
cowplot::plot_grid(plotFull, plot1, plot2, ncol = 2)
# dev.off()
```


Either with one 5th or with one 10th of the locations, the function is still able to detect individual site fidelity as well as the full dataset. This demonstrates the function is robust to different sampling frequencies as well.
