---
title: "ISF test"
author: "Morera-Pujol, Virginia"
date: "July 2021"
output: html_document
---

## Individual site fidelity test

Testing the IndEffectTest function developed for the *Detecting recurrent sources of variability in animal tracking studies* manuscript by Virginia Morera-Pujol *et al.* submitted to Ecological Applications in 2021

### Description

In this document I'll generate, using the package `SIMRiv`, simulated animal movement tracks to test the detection of Individual Site Fidelity by the function developed for the MS "Detecting recurrent sources of variability in animal tracking studies", by Virginia Morera-Pujol et al. (2021), submitted to Ecological Applications. The details of how the tracks with ISF can be simulated can be found [here](https://github.com/VirginiaMorera/Tracking_data_analysis)

Here, we'll run the function once in a dataset of 10 individuals with 10 trips each, with different origins, and once on a dataset of 10 individuals with 10 trips each with the same origin (central place forager scenario).

```{r setup, include = F}
knitr::opts_knit$set(echo = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, 
                     cache = TRUE, fig.width = 12, fig.height = 8)

install.packages("pacman", repos = "http://cran.us.r-project.org")
pacman::p_load(tidyverse, plyr, adehabitatHR, Matching, sf, ctmm, doParallel, foreach, ggpubr,
               geosphere, RColorBrewer, gridExtra, lubridate, SiMRiv, kableExtra, proj4, sp)

'%!in%' <- function(x,y)!('%in%'(x,y))
```


## For animals with different origins

### Generating the data

We use a value for resistance = 1, which means we're simulating maximum ISF (simulated tracks are forced within the template area of no resistance because resistance outside the template area is 1).

```{r ISF test generate prepare,  results = 'hide', echo = TRUE, message = FALSE, warning = FALSE, fig.show = 'hide', cache = TRUE}
set.seed(123)
# set movement parameters of the "species". 
# We're going to configure a Correlated Random walker
CRW <- species(state.CRW(0.3))
test <- simulate(CRW, coords = c(10, 15), time = 100)

# create empty base raster for resistance surfaces
baseRaster <- raster(xmn = -50, xmx = 50, ymn = -50, ymx = 50, res = 0.1)
values(baseRaster) <- 1
baseGrid <- as(baseRaster, "SpatialPixels")
baseGrid@proj4string <- CRS(as.character(NA))

# generate 10 random origin points within a 100000x100000 square, one per "individual"
origin_points <- data.frame(x = runif(10, -25, 25), 
                            y = runif(10, -25, 25))

# simulate 10 trips for each origin (i.e. 10 trips per individual)
template_tracks <- list()
template_UDs <- list()
resistance_surfaces <- list()
simulated_tracks <- list()

for (i in 1:10) {
  # i = 2
  # First we need to create a template trip to get the UD for the resistance surface
  template <- simulate(CRW, coords = c(origin_points[i,1], origin_points[i, 2]), 
                       time = 100)
  template_tracks[i] <- list(template)
  
  spTemplate <- SpatialPoints(coords = template[,1:2], proj4string = baseGrid@proj4string)
  KDE <- kernelUD(spTemplate, h = "href", grid = baseGrid, extent = 2) 
  UD50 <- getverticeshr(KDE, percent = 50)
  template_UDs[i] <- list(UD50) 
  
  # Second, we create the resistance surface
  res_surface <- resistanceFromShape(UD50, baseRaster = baseRaster, field = 0, 
                                     background = 1)
  resistance_surfaces[i] <- list(res_surface)
  
  # Third, we simulate 10 tracks from each surface (i.e. from each individual)
  sim_tracks <- simulate(list(CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW), 
                         start.resistance	= 0,
                         time = 100, resist = res_surface)
  spSim <- SpatialPointsDataFrame(coords = cbind(c(sim_tracks[,1], sim_tracks[,4], 
                                                   sim_tracks[,7], sim_tracks[,10], 
                                                   sim_tracks[,13],sim_tracks[,16],
                                                   sim_tracks[,19], sim_tracks[,22], 
                                                   sim_tracks[,25], sim_tracks[,28]),
                                               c(sim_tracks[,2], sim_tracks[,5], 
                                                 sim_tracks[,8], sim_tracks[,11], 
                                                 sim_tracks[,14], sim_tracks[,17],
                                                 sim_tracks[,20], sim_tracks[,23], 
                                                 sim_tracks[,26], sim_tracks[,29])), 
                                data = data.frame(TrackID = paste(i, 
                                                                  rep(1:10, each = 100),
                                                                  sep = "_"), 
                                                  BirdID = rep(i, 1000)))
  spSim@proj4string <- baseGrid@proj4string
  simulated_tracks[i] <- list(spSim)
  spSim$BirdID <- NULL
  KUD_sim <- kernelUD(spSim, grid = baseGrid)
  
}
```

Now the list `simulated_tracks` has 10 elements, each of them containing the 10 tracks belonging to each "individual". We need to reformat that in a way that we can proceed with the Individual Effect Test

```{r ISF test process, results='hide', echo = TRUE, message=FALSE, warning=FALSE, fig.show='hide'}
list.df <- lapply(seq_along(simulated_tracks),
                  function(i){simulated_tracks[i][[1]]})

# apply rbind to the list
simulated_dataset <- do.call("rbind",
                             list.df)
# assign null projection as X/Y values don't mean anything in this case
simulated_dataset@proj4string <- CRS(as.character(NA))
```

### Visualising the data

```{r ISF test visualise, results='hide', echo = TRUE, message=FALSE, warning=FALSE, fig.width=10.5, fig.height=7}
# first create a version of the data without BirdID to calculate trip overlaps 
sds <- as.data.frame(simulated_dataset)

# convert it in order to be able to plot it 
sdf <- sds %>% 
  st_as_sf(coords = c("coords.x1", "coords.x2")) %>% 
  tidyr::separate(TrackID, into = c("BirdID", "TrackID"), sep = "_") %>% 
  mutate(BirdID = factor(BirdID, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")))

col1 <- ggplot() + 
  geom_sf(data = sdf, aes(col = BirdID), alpha = 0.3, size = 0.7) + 
  xlab("Longitude") + ylab("Latitude") +
  # scale_shape_manual(values = 1:10, guide = "none") +
  theme_bw() + 
  theme(legend.position = "right", legend.box = "horizontal") + 
  guides(col = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  # scale_shape(guide = "none") +
  ggtitle("Simulated positions of 10 non-colonial animals") + 
  NULL 
print(col1)
```

### Testing the function

We now run a simplified version of the function `IndEffectTest` without all the code re the spatial projection, crossing datelines, etc. and as plain code outside the function for easy tweaking.

#### Calculate akde for all tracks and pairwise overlaps

```{r ISF test fun1 run, message = FALSE, warning = FALSE, cache = TRUE, echo = TRUE, eval = FALSE}
# To calculate the overlap we:
# 1 - Turn simulated tracks into "telemetry" objects"
# 2 - fit a guesstimate movement model to each track
# 3 - using the parameters of the guesstimate, fit a series of competing movement models
# 4 - Calculate the debiased BA between top-selected models for each track
# (uncertainty from the model fits is propagated into the overlap estimate under the
#    approximation that the BA is a chi-square random variable)

# 1
sds %>% 
  dplyr::group_by(TrackID) %>%
  dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), ymd_hms('2020-01-30 12:10:00'),
                                length.out = 100)) %>% 
  mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>% 
  dplyr::select(individual.local.identifier = TrackID, 
                Longitude = coords.x1, Latitude = coords.x2, 
                datetime = Date_Time) %>% 
  ungroup() -> sds
sds <- as.data.frame(sds)

sdst <- sds %>% 
  filter(str_detect(individual.local.identifier, "^7")) 

# to remove output from console
message_filename = 'ISF_test_fun1_run_console_output.txt'
try(message_file <- file(message_filename, open="at")) # open file for appending in text mode
sink(message_file, type="message")
sink(message_file, type="output")

sd_tel <- as.telemetry(object = sds, timeformat = "%Y/%m/%d %H:%M:%S")

# FIT.list <- list()
cl <- makeCluster(10, type="PSOCK") ## specify number of cores, and type of cluster (PSOCK or FORK)
registerDoParallel(cl) ## register the backend into a virtual node

before <- Sys.time()

## Execute parallel operation
FIT.list <- foreach(i = 1:length(sd_tel), .packages=c("dplyr", "ctmm", "ggplot2", "lubridate")) %dopar% {
  # print(i)
  one <- sd_tel[[i]]
  # 2
  GUESS <- ctmm.guess(one, interactive=F)
  # 3
  FITS <- ctmm.select(one, GUESS,  trace=TRUE, verbose=TRUE, cores=0)
  print(paste("The selected model for", names(sd_tel)[i], "is", names(FITS)[1], sep = " "))
  x <- FITS[[1]]
}
sink()

Sys.time() - before

# 4
ov <- ctmm::overlap(FIT.list, level = 0.95)
save(FIT.list, ov, file = "testing_function.RDS")
```


#### Obtain median, lower and upper bounds of CI of the overlap and name the matrices with the "BirdID"

The array `ov` contains three "layers", with the median of the overlap distribution in the middle one, and the upper and lower bounds of the CI selected in de function in the first and last. We extract the three matrices from there

```{r ISF test fun2, message = FALSE, warning = FALSE, echo = TRUE}
load("testing_function.RDS")
# separate the layers of the median and CI
X05 <- ov[,,2]
Xlo <- ov[,,1]
Xhi <- ov[,,3]

# remove lower triangle of each (repeated values since it's a symetric matrix)
X05[lower.tri(X05, diag = T)] <- NA
Xlo[lower.tri(Xlo, diag = T)] <- NA
Xhi[lower.tri(Xhi, diag = T)] <- NA


# assign value of BirdID that we rescue from the simulated_dataset df to rows and columns
gid <- simulated_dataset@data[!duplicated(simulated_dataset@data[, "TrackID"]), ][["BirdID"]]
rownames(X05) <- colnames(X05) <- gid
rownames(Xlo) <- colnames(Xlo) <- gid
rownames(Xhi) <- colnames(Xhi) <- gid
```


#### Separate within (WI) and between (BW) group overlaps

The function works by testing how many of the Between Individual overlap CIs contain the median of all the within individual overlaps. It provides three values, the proportion of between individual overlap CIs that contain the median of the WI overlaps, the proportion of BW overlap CIs in which the median of the WI overlaps falls outside of the BW and is higher (above) and the proportion in which is lower (below).

```{r ISF test fun3,  message = FALSE, warning = FALSE, echo = TRUE}
# median
WI05 <- NULL
BW05 <- NULL

# BW lower and higher CI bounds
BWlo <- NULL
BWhi <- NULL

for (i in seq_along(rownames(X05))) {
  # i = 2
  
  # medians
  x1 <- X05[i,] 
  x2 <- x1[which(names(x1) == rownames(X05)[i])]
  x3 <- x1[which(names(x1) != rownames(X05)[i])]
  
  WI05 <- c(WI05, x2)
  BW05 <- c(BW05, x3)
  
  # BW intervals
  y1 <- Xlo[i,] 
  y2 <- y1[which(names(y1) != rownames(Xlo)[i])]
  BWlo <- c(BWlo, y2)
  
  z1 <- Xhi[i,] 
  z2 <- z1[which(names(z1) != rownames(Xhi)[i])]
  BWhi <- c(BWhi, z2)
  
}

# remove NAs
WI05 <- WI05[!is.na(WI05)]
BW05 <- BW05[!is.na(BW05)]
BWlo <- BWlo[!is.na(BWlo)]
BWhi <- BWhi[!is.na(BWhi)]

# organize values in a dataframe for plotting
Overlaps <- data.frame(
  Overlap = c(WI05, BW05),
  Type = c(rep("Within", length(WI05)), rep("Between", length(BW05)))
)
```

### Visualising results

First of all we visualise the different densities of the WI and BW medians (without taking into account CI of individual overlaps)

```{r ISF test fun4,  message = FALSE, warning = FALSE, echo = TRUE}
(plot <- ggplot(data = Overlaps) + 
  geom_density(aes(x = Overlap, col = Type, fill = Type), alpha = 0.5) + 
  ggtitle("Density of within individual vs. between individual median overlaps") +
  theme_bw())
```

### Calculating the WBR (Within-Between ratio)

Now we calculate the median of the WI overlaps, to use as reference values (see if it is contained, above or below the BW CIs)

```{r ISF test fun5,  message = FALSE, warning = FALSE, echo = TRUE}
WI_median <- quantile(WI05, 0.5)

BWint <- data.frame(Low = BWlo,
                    High = BWhi)
```

Finally we produce a one row dataset containing the proportion of Between individual overlaps in which the Within Individual median is below, inside or above the CI.

```{r ISF test fun6,  message = FALSE, warning = FALSE, echo = TRUE}
BWint <- BWint %>% 
    mutate(Contains = "NA") %>% 
    mutate(Contains = if_else(High > WI_median, "NotAbove", "Above (WBR)"))
  
proportions <- as.data.frame(prop.table(table(BWint$Contains)))

names(proportions) <- c("WI_Median_Position", "Percentage")
proportions$Percentage <- round(proportions$Percentage*100, 2)

proportions_wide <- spread(proportions, WI_Median_Position, Percentage)

proportions_wide %>% 
  kable(digits = 2, align = "rrrr") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

The Within-Between Ratio (WBR) is the percenatge of the cases in which the median of the Within Individual overlaps falls above the 95% CI of the between individual overlap distribution. A high WBR indicates that, when run on an artificial dataset, purposely simulating a high degree of individual site fidelity, our function is able to detect individual site fidelity in the simulated dataset.

## For animals with the same origin but different outward angles

### Generating the data

In case of foraging trips of central place foragers, all trips will have the same origin. We create a dataset that simulates those conditions too, to see if the indEffectTest function is still able to detect individual site fidelity.

Again, we simulate the dataset with resistance = 1, which will simulate high ISF conditions

```{r ISF test2 generate data, results = 'hide', message = FALSE, warning = FALSE, fig.show = 'hide', cache = TRUE, echo = TRUE}
set.seed(2106)
CRW <- species(state.CRW(0.2))
test <- simulate(CRW, coords = c(0, 0), time = 100)

# create empty base raster for resistance surfaces
baseRaster <- raster(xmn = -50, xmx = 50, ymn = -50, ymx = 50, res = 0.1)
values(baseRaster) <- 1
baseGrid <- as(baseRaster, "SpatialPixels")

# create a vector of random angles
angles <- runif(10, 0, 360)
# simulate 10 trips for each origin (i.e. 10 trips per individual)
template_tracks <- list()
template_UDs <- list()
resistance_surfaces <- list()
simulated_tracks <- list()

for (i in 1:10) {
  # i = 1
  
  # First we need to create a template trip to get the UD for the resistance surface
  template <- simulate(CRW, coords = c(0, 0), angles = angles[i], time = 100)
  template_tracks[i] <- list(template)
  spTemplate <- SpatialPoints(coords = template[,1:2], proj4string = baseGrid@proj4string)
  KDE <- kernelUD(spTemplate, h = "href", grid = baseGrid) 
  UD50 <- getverticeshr(KDE, percent = 50)
  template_UDs[i] <- list(UD50) 
  # plot(KDE)
  # plot(UD50, add = T)
  # plot(spTemplate, pch = 20, cex = 0.5, add = T)
  
  # Second, we create the resistance surface
  res_surface <- resistanceFromShape(UD50, baseRaster = baseRaster, field = 0, 
                                     background = 1)
  resistance_surfaces[i] <- list(res_surface)
  # plot(res_surface)
  
  # Third, we simulate 10 tracks from each surface (i.e. from each individual)
  sim_tracks <- simulate(list(CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW, CRW), 
                         start.resistance	= 0,
                         time = 100, resist = res_surface)
  spSim <- SpatialPointsDataFrame(coords = cbind(c(sim_tracks[,1], sim_tracks[,4],
                                                   sim_tracks[,7], sim_tracks[,10],
                                                   sim_tracks[,13], sim_tracks[,16],
                                                   sim_tracks[,19], sim_tracks[,22],
                                                   sim_tracks[,25],sim_tracks[,28]),
                                                 c(sim_tracks[,2], sim_tracks[,5],
                                                   sim_tracks[,8], sim_tracks[,11],
                                                   sim_tracks[,14],sim_tracks[,17],
                                                   sim_tracks[,20], sim_tracks[,23],
                                                   sim_tracks[,26], sim_tracks[,29])), 
                                  data = data.frame(TrackID = paste(i, rep(1:10, 
                                                                           each = 100),
                                                                    sep = "_"), 
                                                  BirdID = rep(i, 1000)))
  spSim@proj4string <- baseGrid@proj4string
  simulated_tracks[i] <- list(spSim)
  spSim$BirdID <- NULL
  KUD_sim <- kernelUD(spSim, grid = baseGrid)
    # print(mean(kerneloverlap(spSim, method = "BA", percent = 50, conditional = T)))
  # plot(spSim, add = T, col = spSim$TrackID, pch = 20, cex = 0.5)
}

```

We adapt data to indEffectTest same as before

```{r ISF test2 process,  results = 'hide', message = FALSE, warning = FALSE, fig.show = 'hide', echo = TRUE}
list.df <- lapply(seq_along(simulated_tracks),
                  function(i){simulated_tracks[i][[1]]})

# apply rbind to the list
simulated_dataset <- do.call("rbind",
                             list.df)

# assign null projection as X/Y values don't mean anything in this case
simulated_dataset@proj4string <- CRS(as.character(NA))
```

### Visualising the data

```{r ISF test2 visualise, results = 'hide', message = FALSE, warning = FALSE, echo = TRUE}
# first create a version of the data without BirdID to calculate trip overlaps 
sds <- as.data.frame(simulated_dataset)

# convert it in order to be able to plot it 
sdf <- sds %>% 
  st_as_sf(coords = c("coords.x1", "coords.x2")) %>% 
  tidyr::separate(TrackID, into = c("BirdID", "TrackID"), sep = "_") %>% 
  mutate(BirdID = factor(BirdID, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")))

col2 <- ggplot() + 
  geom_sf(data = sdf, aes(col = BirdID), alpha = 0.3, size = 0.7) + 
  xlab("Longitude") + ylab("Latitude") +
  # scale_shape_manual(values = 1:10) +
  theme_bw() + 
  theme(legend.position = "right", legend.box = "horizontal") + 
  guides(col = guide_legend(override.aes = list(size = 3, alpha = 1))) +
  ggtitle("Simulated positions of 10 colonial animals") + 
  NULL
print(col2)
```

### Testing the function

#### Calculate akde for all tracks and pairwise overlaps

```{r ISF test2 fun1, results = 'hide', message = FALSE, warning = FALSE, fig.show = 'hide', echo = TRUE, eval = FALSE}
# To calculate the overlap we:
# 1 - Turn simulated tracks into "telemetry" objects"
# 2 - fit a guesstimate movement model to each track
# 3 - using the parameters of the guesstimate, fit a series of competing movement models
# 4 - Calculate the debiased BA between top-selected models for each track
# (uncertainty from the model fits is propagated into the overlap estimate under the
#     approximation that the BA is a chi-square random variable)

# 1
sds %>% 
  dplyr::group_by(TrackID) %>%
  dplyr::mutate(Date_Time = seq(ymd_hms('2019-11-30 12:10:00'), ymd_hms('2020-01-30 12:10:00'),
                                length.out = 100)) %>% 
  mutate(Date_Time = format(Date_Time, format = "%Y/%m/%d %H:%M:%S", tz = "UTC")) %>% 
  dplyr::select(individual.local.identifier = TrackID, 
                Longitude = coords.x1, Latitude = coords.x2, 
                datetime = Date_Time) %>% 
  ungroup() -> sds
sds <- as.data.frame(sds)

message_filename = 'script_messages.txt'
try(message_file <- file(message_filename, open="at")) # open file for appending in text mode
sink(message_file, type="message")
sink(message_file, type="output")

sd_tel <- as.telemetry(object = sds, timeformat = "%Y/%m/%d %H:%M:%S")


# FIT.list <- list()
cl <- makeCluster(10, type="PSOCK") ## specify number of cores, and type of cluster (PSOCK or FORK)
registerDoParallel(cl) ## register the backend into a virtual node

before <- Sys.time()

## Execute parallel operation
FIT.list <- foreach(i = 1:length(sd_tel), .packages=c("dplyr", "ctmm", "ggplot2", "lubridate")) %dopar% {
  #  print(i)
  one <- sd_tel[[i]]
  # 2
  GUESS <- ctmm.guess(one, interactive=F)
  # 3
  FITS <- ctmm.select(one, GUESS,  trace=TRUE, verbose=TRUE, cores=0)
  print(paste("The selected model for", names(sd_tel)[i], "is", names(FITS)[1], sep = " "))
  x <- FITS[[1]]
}
sink()
Sys.time() - before

# 4
ov <- ctmm::overlap(FIT.list, level = 0.95)

save(FIT.list, ov, file = "testing_function2.RDS")
```


#### Obtain median, lower and upper bounds of CI of the overlap and name the matrices with the "BirdID"

The array `ov` contains three "layers", with the median of the overlap distribution in the middle one, and the upper and lower bounds of the CI selected in de function in the first and last. We extract the three matrices from there

```{r ISF test2 fun2, results = 'hide', message = FALSE, warning = FALSE, fig.show = 'hide', echo = TRUE}
load("testing_function2.RDS")
# separate the layers of the median and CI
X05 <- ov[,,2]
Xlo <- ov[,,1]
Xhi <- ov[,,3]

# remove lower triangle of each (repeated values since it's a symetric matrix)
X05[lower.tri(X05, diag = T)] <- NA
Xlo[lower.tri(Xlo, diag = T)] <- NA
Xhi[lower.tri(Xhi, diag = T)] <- NA

# assign value of BirdID that we rescue from the simulated_dataset df to rows and columns
gid <- simulated_dataset@data[!duplicated(simulated_dataset@data[, "TrackID"]), ][["BirdID"]]
rownames(X05) <- colnames(X05) <- gid
rownames(Xlo) <- colnames(Xlo) <- gid
rownames(Xhi) <- colnames(Xhi) <- gid
```


#### Separate within (WI) and between (BW) group overlaps

The function works by testing how many of the Between Individual overlap CIs contain the median of all the within individual overlaps. It provides three values, the proportion of between individual overlap CIs that contain the median of the WI overlaps, the proportion of BW overlap CIs in which the median of the WI overlaps falls outside of the BW and is higher (above) and the proportion in which is lower (below).

```{r ISF test2 fun3, results = 'hide', message = FALSE, warning = FALSE, fig.show = 'hide', echo = TRUE}
# mediana
WI05 <- NULL
BW05 <- NULL

# BW lower and higher CI bounds
BWlo <- NULL
BWhi <- NULL

for (i in seq_along(rownames(X05))) {
  # i = 2
  # medians
  x1 <- X05[i,] 
  x2 <- x1[which(names(x1) == rownames(X05)[i])]
  x3 <- x1[which(names(x1) != rownames(X05)[i])]
  
  WI05 <- c(WI05, x2)
  BW05 <- c(BW05, x3)
  
  # BW intervals
  y1 <- Xlo[i,] 
  y2 <- y1[which(names(y1) != rownames(Xlo)[i])]
  BWlo <- c(BWlo, y2)
  
  z1 <- Xhi[i,] 
  z2 <- z1[which(names(z1) != rownames(Xhi)[i])]
  BWhi <- c(BWhi, z2)
  
}

# remove NAs
WI05 <- WI05[!is.na(WI05)]
BW05 <- BW05[!is.na(BW05)]
BWlo <- BWlo[!is.na(BWlo)]
BWhi <- BWhi[!is.na(BWhi)]

# organize values in a dataframe for plotting
Overlaps <- data.frame(
  Overlap = c(WI05, BW05),
  Type = c(rep("Within", length(WI05)), rep("Between", length(BW05)))
)
```


### Visualising results

First of all we visualise the different densities of the WI and BW medians (without taking into account CI of individual overlaps)

```{r ISF test2 fun4,  message = FALSE, warning = FALSE, echo = TRUE}
(plot <- ggplot(data = Overlaps) + 
  geom_density(aes(x = Overlap, col = Type, fill = Type), alpha = 0.5) + 
  ggtitle("Density of within individual vs. between individual median overlaps") +
  theme_bw())
```


### Calculating the WBR (Within-Between ratio)

Now we calculate the median of the WI overlaps, to use as reference values (see if it is contained, above or below the BW CIs)

```{r ISF test2 fun5,  message = FALSE, warning = FALSE, echo = TRUE}
WI_median <- quantile(WI05, 0.5)

BWint <- data.frame(Low = BWlo,
                    High = BWhi)
```

Finally we produce a one row dataset containing the proportion of Between individual overlaps in which the Within Individual median is below, inside or above the CI.

```{r ISF test2 fun6,  message = FALSE, warning = FALSE, echo = TRUE}
BWint <- BWint %>% 
    mutate(Contains = "NA") %>% 
    mutate(Contains = if_else(High > WI_median, "NotAbove", "Above (WBR)"))
  
proportions <- as.data.frame(prop.table(table(BWint$Contains)))

names(proportions) <- c("WI_Median_Position", "Percentage")
proportions$Percentage <- round(proportions$Percentage*100, 2)

proportions_wide <- spread(proportions, WI_Median_Position, Percentage)

proportions_wide %>% 
  kable(digits = 2, align = "rrrr") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

The Within-Between Ratio (WBR) is the percenatge of the cases in which the median of the Within Individual overlaps falls above the 95% CI of the between individual overlap distribution. A high WBR indicates that, when run on an artificial dataset, purposely simulating a high degree of individual site fidelity, our function is able to detect individual site fidelity in the simulated dataset.

